The \project{unRAVE} catalog

### 2016-09-05 article/unrave.tex
Include training set source in abstract; claim improvement over DR4. Closes #16 #17

\begin{abstract}
The Milky Way is a powerful laboratory for understanding galaxy formation,
as it can provide orbits, ages, physical parameters, as well as chemical 
abundances for vast sets of individual stars.  These inferences require 
both astrometric and spectroscopic data.  Indeed, in order to be maximally
useful for chemo-dynamic studies, the Tycho-Gaia Astrometric Solution 
(\tgas) sample in the first \gaia\ data release requires a spectroscopic 
complement that includes radial velocities, stellar parameters, and 
elemental abundances.  Among existing spectroscopic samples, the RAdial 
Velocity Experiment (\rave) survey has the largest overlap with \tgas: 
292,036 stars.  Here we present a data-driven re-analysis of \rave\ 
spectra, using an implementation of \thecannon, that yields more precise 
and accurate stellar parameters and abundances.  We derive, and validate
improved effective temperature $\teff$, surface gravity $\logg$, and 
chemical abundances of up to seven elements (O, Mg, Al, Si, Ca, Fe, Ni) 
for \Nstarsqc\ stars.  The typical precision in chemical abundances is 
X.XX~dex for stars on the giant branch.  
The \unrave\ catalog presented here, in conjunction with \tgas, represents the most powerful data set for chemo-orbital analysis at the dawn of 
broadly available \gaia\ data.
\end{abstract}

@@

We have presented the largest collection of stellar abundances for stars in the 
first \gaia\ data release.  In total more than X.XX million abundances are
available, with effective temperature $\teff$, surface gravity $\logg$ and 
metallicity available for XXXXXX stars.  Despite the caveats and limitations 
discussed here, our validation experiments and comparisons with high-resolution
spectroscopic studies suggests that our results have sufficient accuracy and
precision to be useful for exoplanet host stars studies 
\citep[c.f.,][]{Valenti_Fischer_2005}, investigations of the Milky Way disk 
\citep[c.f.,][]{Reddy_2003,Reddy_2006,Bensby_2014}, and a multitude of 
chemo-dynamic studies.  When combined with positions and 3D velocities from \gaia,
we are optimistic that the \project{unRAVE} catalog will help advance understanding 
of the Milky Way's formation and evolution.

>>>>

\begin{abstract}
The Milky Way is a powerful laboratory for understanding galaxy formation,
as it can provide orbits, ages, physical parameters, as well as chemical 
abundances for vast sets of individual stars.  These inferences require 
both astrometric and spectroscopic data.  Indeed, in order to be maximally
useful for chemo-dynamic studies, the Tycho-Gaia Astrometric Solution 
(\tgas) sample in the first \gaia\ data release requires a spectroscopic 
complement that includes radial velocities, stellar parameters, and 
elemental abundances.  Among existing spectroscopic samples, the RAdial 
Velocity Experiment (\rave) survey has the largest overlap with \tgas: 
292,036 stars.  Here we present a data-driven re-analysis of \rave\ 
spectra, using an implementation of \thecannon, that yields more precise 
and accurate stellar parameters and abundances than previous \rave\
data releases.  We constructed our model using high-fidelity \apogee\ 
stellar parameters and abundances for red giant branch stars that overlap
with \rave, and stellar parameters from the \project{K2}/\project{Ecliptic 
Pole Input Catalog} for main-sequence and sub-giant branch stars.
We derive, and validate, improved effective temperature $\teff$, surface 
gravity $\logg$, and chemical abundances of up to seven elements (O, Mg, 
Al, Si, Ca, Fe, Ni) for \Nstarsqc\ stars.  The typical precision in 
chemical abundances is X.XX~dex for red giant branch stars.  The \unrave\ 
catalog presented here, in conjunction with \tgas, represents the 
most powerful data set for chemo-orbital analysis at the dawn of broadly 
available \gaia\ data.
\end{abstract}

@@

We have presented the largest collection of stellar abundances for stars in the 
first \gaia\ data release.  In total more than X.XX million abundances are
available, with effective temperature $\teff$, surface gravity $\logg$ and 
metallicity available for XXXXXX stars.  Despite the caveats and limitations 
discussed here, our validation experiments and comparisons with high-resolution
spectroscopic studies suggests that our results have sufficient accuracy and
precision to be useful for exoplanet host stars studies 
\citep[c.f.,][]{Valenti_Fischer_2005}, investigations of the Milky Way disk 
\citep[c.f.,][]{Reddy_2003,Reddy_2006,Bensby_2014}, and a multitude of 
chemo-dynamic studies.  When combined with positions and 3D velocities from \gaia,
we are optimistic that the \unrave\ catalog will help advance understanding 
of the Milky Way's formation and evolution.
